### 2021-04-06 papers/SYRCoSE/future.tex
SYRCoSE: minor fixes

First, we plan to apply our library to a wider range of problems. 
We are going to develop a mechanized semantics of some classical 
languages used to model concurrency, in particular 
the calculus of communicating systems~(CCS)~\cite{Milner:80} and 
$\pi$-calculus~\cite{Milner:99}.      
We also plan to continue our work on 
expressing various relaxed models 
of shared memory~\cite{Sewell-al:CACM10, Lahav-al:POPL16, Lahav-al:PLDI17, Podkopaev-al:POPL19}
in terms of event structures.

>>>>

First, we plan to apply our library to a wider range of problems. 
We are going to develop a mechanized semantics of some classical 
languages used to model concurrency, in particular 
the calculus of communicating systems~(CCS)~\cite{Milner:80} and 
$\pi$-calculus~\cite{Milner:99}.      
We also plan to continue our work on 
expressing various relaxed models 
of shared memory~\cite{Lahav-al:POPL16, Lahav-al:PLDI17, Podkopaev-al:POPL19}
in terms of event structures.

### 2021-04-06 papers/SYRCoSE/intro.tex
SYRCoSE: WIP --- reworking text
SYRCoSE: minor fixes

Event structures is a mathematical formalism introduced 
by Winskel~\cite{Winskel:86} as a semantic domain of concurrent programs.
In recent years there is a renewed interest in event structures, 
with the applications of the theory ranging from relaxed memory models%
~\cite{Jeffrey-Riely:LICS16, PichonPharabod-Sewell:POPL16, Chakraborty-Vafeiadis:POPL19}
to model-based mutation testing~\cite{Fellner-al:VMCAI2020}.
\eupp{perhaps, we could add more citations once the related work is ready.}

@@

Under the interleaving semantics 
it has $3! = 6$ traces with each trace consisting of $4$ events,
as depicted on \cref{fig:intro-traces}.
Event themselves represent atomic side-effects 
of instructions' execution. In our case 
it is either a write of a value to a shared variable $\wlab{x}{a}$,
or a read of a particular value from a shared variable $\rlab{x}{a}$.

@@

In the programming language and formal semantics research community 
it becomes the de-facto standard to complement the theoretical 
studies with their mechanization in the \emph{proof assistants}
like Coq, Agda, Isabelle, Arend, and others,
as this process increases the reliability and reproducibility 
of the scientific results.
Yet, as far as we know, there is a little work on 
mechanization of event structures theory.

>>>>

Event structures is a mathematical formalism introduced 
by Winskel~\cite{Winskel:86} as a semantic domain of concurrent programs.
In recent years there is a renewed interest in event structures, 
with the applications of the theory ranging from relaxed memory models%
~\cite{Jeffrey-Riely:LICS16, PichonPharabod-Sewell:POPL16, Chakraborty-Vafeiadis:POPL19}
to model-based mutation testing~\cite{Fellner-al:VMCAI2020}.
% \eupp{perhaps, we could add more citations once the related work is ready.}

@@

Under the interleaving semantics 
it has $3! = 6$ traces with each trace consisting of $4$ events,
as depicted on \cref{fig:intro-traces}.
Event themselves represent atomic side-effects produced by the execution of instruction. 
In our case it is either a write of a value to a shared variable $\wlab{x}{a}$,
or a read of a particular value from a shared variable $\rlab{x}{a}$.

@@

In the programming language and formal semantics research communities 
it becomes the de-facto standard to complement the theoretical 
studies with their mechanization in the \emph{proof assistants}
like Coq, Agda, Isabelle, Arend, and others,
as this process increases the reliability and reproducibility 
of the scientific results.
Yet, as far as we know, there is a little work on 
mechanization of event structures theory.

### 2021-04-06 papers/SYRCoSE/regmachine-eventstruct.tex
SYRCoSE: minor fixes

Next, following the theory of axiomatic weak memory models~\cite{\todo{}},
we define the causality relation of the register machine's event structure
as a transitive closure of two relations~---~\emph{program order} 
and \emph{reads-from}, denoted as $\lPO$ and $\lRF$ correspondingly.

@@

Program order tracks precedence of events within a single thread. 
Reads-from relation captures the flow of values from 
write events to read events, and ensures that values 
do not appear out of thin-air~\cite{\todo{}}.

@@

>>>>

Next, following the theory of axiomatic weak memory models~\cite{Lahav-al:PLDI17},
we define the causality relation of the register machine's event structure
as a transitive closure of two relations~---~\emph{program order} 
and \emph{reads-from}, denoted as $\lPO$ and $\lRF$ correspondingly.

@@

Program order tracks precedence of events within a single thread. 
Reads-from relation captures the flow of values from 
write events to read events, and ensures that values 
do not appear out of thin-air~\cite{Boehm-Demsky:MSPC14, Lahav-al:PLDI17}.

@@

On \cref{fig:eventstruct-example} one can see the prime event structure
obtained as a result of incremental construction 
depicted on \cref{fig:regmachine-eventstruct-example}.

\input{fig/eventstruct-example.tex}

Once the event structure is constructed, one can extract
the configurations corresponding to the particular runs 
of the parallel register machine, and 
further filter them via \emph{consistency predicate}
defining the \emph{memory consistency model}.
Our construction of the event structures allows to encode 
a wide class of so-called $\lPO\cup\lRF$ acyclic 
relaxed memory models~\cite{Lahav-al:PLDI17}.
